data_preparation

### 2024-03-25 src/data_prep/data_prep.Rmd

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(tidyr)
library(dplyr)
library(stringr)
library(rmarkdown)
```

>>>>

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(tidyr)
library(dplyr)
library(stringr)
library(rmarkdown)
library(tinytex)
library(pdftools)
library(latexpdf)
library(latexdiffr) 
```
